---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "Emilie Xiao"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_count, aes(x = date, y = Cases)) + geom_point()
```



If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```

1. Write code for a plot and describe what you observe?
```{r}
ggplot(covid_data_count, aes(x = race, y = Cases)) +
  geom_bar(stat = "identity", fill = "pink")
```
Among all races across the US, white people had the highest amount of COVID cases. 

2. Are there any conclusions you can draw?
Not quite, this is not the best representation of the numbers to draw conclusions.

3. What were you not able to do due to not having the R knowledge?
I was unable to calculate the proportion of cases / population into a new column to get a better estimate. 

4. What other data would be useful to better understand this data?
I think tracking vaccination or age data might be some additional helpful information to analyze.
